Exploring Alternative Routes Using Multipath TCP

### 2017-06-05 paper/presentation.tex
paper,presentation: update Topology and AWS figures
presentation: future work
paper: reorder conclusion/fw. this is the last commit of presentation!

\TitledFigureSlide{figures/Concept.pdf}{Concept}{
  \begin{itemize}
  \item Detour routing has shown promise for a long time
  \item Some applications have been able to leverage it (e.g. Bittorrent)
  \item However, few unmodified applications may use the detour routing strategy
  \item Our concept is to use MPTCP to achieve detour routing in unmodified
    applications
  \item We use tunneling mechanisms to put a subflow across a detour host
  \end{itemize}
}

@@

  \begin{itemize}
  \item OpenVPN Approach
    \begin{itemize}
    \item Establish an OpenVPN connection with detour
    \item Send packets as normal through the virtual interface
    \item Packets encapsulated via OpenVPN protocol
    \item Detour still performs NAT
    \end{itemize}
  \item NAT Approach
    \begin{itemize}
    \item Address packets directly to detour
    \item Detour alters source and destination address, forwards packet
    \item Address information must be arranged ahead of time
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\FigureSlide{figures/Topology.pdf}{
  \begin{itemize}
  \item This is network topology we us
  \item Has path diversity, a client, a server, a detour
  \item Each link has 5ms delay.
  \end{itemize}
}

@@

  \begin{itemize}
  \item Deployed client, server, and detour implementations to different AWS
    regions
  \item Ran similar throughput measurements for MPTCP
  \item Performed at much higer level, but didn't show similar improvements
  \end{itemize}
\end{frame}

@@

@@

  \begin{itemize}
  \item Detour Collective
  \item Dynamic subflow addition and removal
  \item Data scheduling
  \end{itemize}
\end{frame}

  \begin{itemize}
  \item Created a system for adding detour routes to MPTCP connections between
    single-homed devices.
  \item Like MPTCP, this system works outside of experimental networks
  \item System is capable of achieving similar performance to the best available
    path when no aggregation is possible
  \item System is capable of aggregating throughput when possible
  \end{itemize}
\end{frame}

\appendix % slide numbering includes nothing after here

>>>>

\TitledFigureSlide{figures/Concept.pdf}{Concept}{
  \begin{itemize}
  \item Detour routing has shown promise for a long time
  \item Some applications have been able to leverage it (e.g. Bittorrent)
  \item However, few unmodified applications may use the detour routing strategy
  \item Our concept is to use MPTCP to achieve detour routing in unmodified
    applications
  \item We use tunneling mechanisms to put a subflow across a detour host
  \item Deployment scenario: friends with high bandwidth form a collective,
    offer each other detouring services.
  \end{itemize}
}

@@

  \begin{itemize}
  \item OpenVPN Approach
    \begin{itemize}
    \item Establish an OpenVPN connection with detour
    \item Send packets as normal through the virtual interface
    \item Packets encapsulated via OpenVPN protocol
    \end{itemize}
  \item NAT Approach
    \begin{itemize}
    \item Address packets directly to detour
    \item Detour alters source and destination address, forwards packet
    \item Address information must be arranged ahead of time
    \end{itemize}
  \end{itemize}
\end{frame}

@@

\FigureSlide{figures/Topology.pdf}{
  \begin{itemize}
  \item This is network topology we us
  \item Has path diversity, a client, a server, a detour
  \item Each link has 5ms delay.
  \item Core links red, access links blue
  \end{itemize}
}

@@

  \begin{itemize}
  \item Deployed client, server, and detour implementations to different AWS
    regions
  \item Ran similar throughput measurements for MPTCP
  \item Performed at much higer level, but didn't show similar improvements
  \item OpenVPN cannot sustain above 60Mbps in our setup
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item Created a system for adding detour routes to MPTCP connections between
    single-homed devices.
  \item Like MPTCP, this system works with unmodified applications
  \item System is capable of achieving similar performance to the best available
    path when no aggregation is possible
  \item System is capable of aggregating throughput when possible
  \end{itemize}
\end{frame}

@@

  \begin{itemize}
  \item Deployment scenarios
  \item Dynamic subflow addition and removal
  \item Data scheduling
  \item 0-RTT NAT establishment
  \end{itemize}
\end{frame}

\appendix % slide numbering resets here
